Figures

### 2019-04-24 code/figures.rmd
End-polishing of figures

@@

# save_plot("../figures/densities_het.png", densities,
     #      nrow = 2, base_height = 5, base_width = 5, dpi = 600)
```

@@

tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))

effect_het <- plot_grid(I2, H2, tau2, ncol = 1, align = "v", rel_heights = c(0.86, 0.86, 1)) #combine plots
effect_het
#save_plot("../figures/effect-het.png", effect_het,
#          ncol = 1, base_height = 7, base_width = 5, dpi = 600)

>>>>

```
Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 37 effects. Tau is not directly comparable across effect size measures.

@@

# save_plot("../figures/densities_het.png", densities,
           # nrow = 2,  base_width = 7, base_aspect_ratio = 0.618, dpi = 600)
```
Figure 2. Simulated $I^2$ (a) and $/tau^2$ (b) densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed I2 estimates for the 37 effects. For panel b) effects consist of correlations and biserial correlation and heterogeneity levels were approximated by Fisher’s z values corresponding to Higgins’ definitions for the median sample size of 108. Each simulated density consists of approximately 370,000 estimates.

@@

tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(tau)^2, " estimate"))) +
  scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))

effect_het <- plot_grid(I2, H2, tau2, ncol = 1, align = "v", rel_heights = c(0.86, 0.86, 1), labels = c("a", "b", "c")) #combine plots
effect_het
# save_plot("../figures/effect-het.png", effect_het,
         # ncol = 1, base_height = 7, base_width = 5, dpi = 600)

```
Figure 3. The correlation between a) I2 ,and effect size and b) H2 and c)  τ ̂^2and effect size for 37 effects from ten pre-registered multi-lab replication projects. Shaded bands represent 95% confidence intervals
